My Past Work

### 2025-01-28 interests.qmd
Desktop View
Update

### (1) SlideCraft - AI Design Tool - [Try](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)

@@

[![](src/images/Slidecraft.png)](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)

@@

#### Desktop View - [Try](https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1)

[![](src/images/GPTDashboard.png)](https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1)

#### Mobile View - [Try](https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1)

[![](src/images/Mobile Dashboard.png)](https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1)

### (3) SaveWatt - [Try](https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1)

@@

This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way.

Full PortFolio: <https://savewatt.framer.website>

@@

[![](src/images/SaveWatt_Prototype.png)](https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1)

>>>>

### (1) SlideCraft - AI Design Tool - <a href="https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1" target="_blank">Try</a>

@@

![](src/images/Slidecraft.png)

@@

#### Desktop View - <a href="https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1" target="_blank">Try</a>

![](src/images/GPTDashboard.png)

#### Mobile View - <a href="https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1" target="_blank">Try</a>

![](src/images/Mobile%20Dashboard.png)

### (3) SaveWatt - <a href="https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1" target="_blank">Try</a>

@@

![](src/images/SaveWatt_Prototype.png)

This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way.Full PortFolio: <https://savewatt.framer.website> (Use Desktop View only)

@@
